Do Automated Fault Localization Techniques Work For REST APIs?

### 2024-05-28 CS563-Project/Paper/paper.tex
Added a rough figure to the paper for now, needs updating the figure along the text for detailed explanation

@@

The dataset we started with had  GitHub APIs from 15 different REST API repositories from 
% Table ~\ref{tab:repositories}. 
the services were management-api-for-apache-cassandra, catwatch, cwa-verification-server, digdag, enviroCar-server, features-service,
gravitee-api-management, kafka-rest, ocvn, ohsome-api, proxyprint-kitchen, quartz-manager, restcountries, senzing-api-server, and Ur-Codebin-API.
The  process of filtering out issues not marked as 'bugs' and 'closed,' leaving only the set of issues that have been fixed details ~\ref{tab:repositories}. Issues involving code changes are collected and then further filtered through manual analysis to select those applicable to this research.

@@

This dataset provides a benchmark to evaluate FL techniques on REST API faults.

>>>>

\begin{figure*}[t] 
    \centering
    \includegraphics[width=1.0\textwidth]{fig2.png}
    \caption{Approach Overview}
    \label{fig:widefigure}
  \end{figure*}

@@

The dataset we started with had  GitHub APIs from 15 different REST API repositories from the services were management-api-for-apache-cassandra, catwatch, cwa-verification-server, digdag, enviroCar-server, features-service,
gravitee-api-management, kafka-rest, ocvn, ohsome-api, proxyprint-kitchen, quartz-manager, restcountries, senzing-api-server, and Ur-Codebin-API.
The  process of filtering out issues not marked as 'bugs' and 'closed,' leaving only the set of issues that have been fixed details ~\ref{tab:repositories}. Issues involving code changes are collected and then further filtered through manual analysis to select those applicable to this research. These services provide us services with bug information we need to create a benchmark on REST API faults.

@@
